PM Component Paper Plots

### 2021-11-09 code/data-viz/forest-plots-color-shape.Rmd
2nd Rev - Mortality Rate - ExpoBuffer PM results
graphical abs revise

---
title: "PM Component Paper Plots"
author: "Fatemeh Kazemi"
date: "02-13-2021"
---

@@

p <- ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
    geom_vline(xintercept = 1, linetype = 2, color = "black") +
    geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
                 color = plot.cols, size = 0.25, show.legend = F) + 
    geom_point(aes(x = HR, y = Index, shape = sig), 
               color = plot.cols, size = 1.5, show.legend = F) +
  labs(x = "HR (95% CI) per IQR Increase", y = expression(paste("Source-Related ", PM[2.5])),
       title = expression(paste("Association of Long-Term Source-Related ", PM[2.5], " Exposure and Cause-Specific Mortality"))) +
    scale_shape_identity() +
    facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
   theme_bw() + 
    theme(panel.spacing.x = unit(0.5, 'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(face = 'bold', color = "black"),
        strip.background = element_rect(fill = "#B9CFED"),
        axis.title = element_text(size = 12, color = 'black'),
        axis.text = element_text(size = 9, color = 'black'),
        plot.title = element_text(size = 12, face = 'bold', color = 'black', hjust = 0.5, vjust = 2))

>>>>

---
title: "PM Component Paper Plots"
author: "Fatemeh Kazemi"
date: "10-17-2021"
---

@@

p <- ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
    geom_vline(xintercept = 1, linetype = 2, color = "black") +
    geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
                 color = plot.cols, size = 0.25, show.legend = F) + 
    geom_point(aes(x = HR, y = Index, shape = sig), 
               color = plot.cols, size = 1.5, show.legend = F) +
  labs(x = "HR (95% CI) per IQR Increase", y = "",
       #expression(paste("Source-Related ", PM[2.5]))
       title = expression(paste("Association of Long-Term Source-Related ", PM[2.5], " Exposure and Cause-Specific Mortality"))) +
    scale_shape_identity() +
    facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
   theme_bw() + 
    theme(panel.spacing.x = unit(0.5, 'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(face = 'bold', color = "black"),
        strip.background = element_rect(fill = "#B9CFED"),
        axis.title = element_text(size = 10, color = 'black'),
        axis.text = element_text(size = 9, color = 'black'),
        plot.title = element_text(size = 12, face = 'bold', color = 'black', hjust = 0.5, vjust = 2))
